\clearpage
\null
\vfil
\thispagestyle{plain}
\begin{center}\textbf{Abstract}\end{center}
% The same is true for cloud storage, where the well-known trade-off between cost and latency is the driving factor for various services. 
% The popularity of cloud-based services is leading to an increasing number of different services that are evolving to accommodate the diverse requirements. The same applies to cloud storage: the various services are optimized for a certain level in terms of the trade-off between cost and latency. Latency is critical to the user experience. Therefore, it is important to keep end-to-end latency as low as possible across the entire technology stack. The same is true for cloud storage, where in-memory caching can play a critical role in meeting desired latency requirements. Current fully managed in-memory caching systems suffer from the low flexibility of their pricing model in specific settings. In this work, we combine a well-known in-memory caching technology with serverless computing to build a managed system. Serverless computing enables our reactive system design to provide responsiveness, which is critical in terms of cost and latency. We demonstrate the applicability of serverless computing in a novel approach to providing in-memory caching. Our system outperforms managed services in certain conditions and achieves high in-memory percentages despite its reactive approach.
Cloud-based services are becoming increasingly popular, with many new services emerging or existing services being adapted to current requirements. The same applies to cloud storage: the various services are optimized for a certain level regarding the trade-off between cost and latency. Latency is critical to the user experience, so it is essential to keep end-to-end latency as low as possible across the technology stack. Cloud storage is no exception, and in-memory caching can play a critical role in meeting desired latency requirements. Current fully managed in-memory caching systems suffer from the low flexibility of their pricing model in specific settings. In this work, we combine a well-known in-memory caching technology with serverless computing to build a custom managed system. Serverless computing enables our reactive system design to provide responsiveness through fast spin-up times, which is critical in terms of cost and latency. We demonstrate the applicability of serverless computing in a novel approach to providing in-memory caching. The results show that our reactive design with serverless computing can outperform managed services under certain conditions and achieve high cache hit rates despite its reactive approach.
\vfil
\clearpage 
